### 2020-02-11 ChapterIntroduction/chapterIntroduction.tex
Fixed: References

\section{Scalable Games and Simulations}
Scaling and more complex games are a selling point. This has been demonstrated by games such as EVE Aether Wars \cite{AetherWars} and \cite{WorldsAd48:online}, built using HadeanOS and SpatialOS respectively. HadeanOS and SpatialOS both provide attempts at distributing physics by allowing physical interactions across servers. Despite the growing commercial interest in this area, there is no academic literature into the challenges and solutions of distributed real-time physics and HadeanOS and SpatialOS are both proprietary software.

>>>>

\section{Scalable Games and Simulations}
Scaling and more complex games are a selling point. This has been demonstrated by games such as EVE Aether Wars \cite{AetherEngine} and \cite{WorldsAd48:online}, built using HadeanOS and SpatialOS respectively. HadeanOS and SpatialOS both provide attempts at distributing physics by allowing physical interactions across servers. Despite the growing commercial interest in this area, there is no academic literature into the challenges and solutions of distributed real-time physics and HadeanOS and SpatialOS are both proprietary software.
